---
title: "Untitled"
date: "24 Februar 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = '/Users/Antoine/Documents/biostat/data')
```

## Exercise 3
The file farm.dat contains the size A (in acres), the number of cows C and the income I
(in $) of 20 farms in the US. You find the data set on ILIAS.

a) Compute an ordinary linear regression of I versus C. Does the income depend on the number of
cows?
```{r}

farm <- read.table("farm.dat",header = T)
lm1 <- lm(Dollar~cows,farm)
summary(lm1)
```
There is a significant p-value of 0.000475 of cows on income. 


b) Give the confidence intervals for the expected income without any cows, with 20 cows, and with C = 8.85 cows.
```{r}
predict(lm1, newdata=data.frame(cows=c(0,20,8.85)), interval="confidence")
```

c) Compute an ordinary linear regression of I versus A and a multiple linear regression of I versus
A and C. Also compute the correlation between A and C. Finally, based on your results, explain
the differences between the three regression models.
```{r}
lm2 <- lm(Dollar~acres,farm)
lm3 <- lm(Dollar~cows+acres,farm)
summary(lm2)
summary(lm3)
```
The number of acres itself has no influence on the income of a farmer. However, combined the cows compensate for the negative effect and the effect of them together is even stronger.
```{r}
cor(farm$cows,farm$acres)
```


## Exercise 4
In this exercise, we again consider the air pollution data set presented in the lecture. In
a study on the contribution of air pollution to mortality, General Motors collected data from 60
US cities. The dependent variable is the age adjusted mortality (variable Mortality). The data
includes variables measuring demographic characteristics of the cities, variables measuring climate
characteristics, and variables recording the pollution potential of three different air pollutants.

a) Get an overview of the data and account for possible problems. Which of the variables need to
be transformed?
```{r, echo=F}
airpollution <- read.csv('airpollution.csv');airpollution
dim(airpollution)
par(mfrow=c(4,4))
for (i in 2:length(airpollution)){
  hist(airpollution[,i],main = names(airpollution[i]))
}
```
Transform the following traits: 
```{r}
airpollution$Pop <- log(airpollution$Pop)
airpollution$HC <- log(airpollution$HC)
airpollution$NOx <- log(airpollution$NOx)
airpollution$SO2 <- log(airpollution$SO2)

names(airpollution)[names(airpollution)=="Pop"]<-"logPop"
names(airpollution)[names(airpollution)=="HC"]<- "logHC"
names(airpollution)[names(airpollution)=="NOx"]<-"logNOx"
names(airpollution)[names(airpollution)=="SO2"]<-"logSO2"

```

b) Carry out a multiple linear regression containing all variables. Does the model fit well? Check
the residuals.
```{r}
# Exclude the city names
airpollution <- airpollution[,c(2:length(airpollution))]
# Calculate the Multiple linear regression model
lmairpollution <- lm(Mortality~.,airpollution)
summary(lmairpollution)
```
Check the fit of the model:
```{r}

library(car)
par(mfrow=c(1,2))
#par(mfrow = c(1, 2), mar = c(1.5, 2, 1.5, 0.5), cex = 0.5)
plot(fitted(lmairpollution),resid(lmairpollution),xlab = "Fittings",ylab = "Residuals",main = "Tukey-Anscombe-Plot of all airpollution variables")
qqPlot(resid(lmairpollution),dist="norm",mean=mean(resid(lmairpollution)),sd=sd(resid(lmairpollution)))
```
The model seems to fit very well. Not all variables are significant.


c) Now take all the non-significant variables out of the model and compute the regression again.
Compare your results to part b.).
```{r}
lmap_sign <- lm(Mortality~JanTemp+Rain+NonWhite+logNOx,airpollution)
summary(lmap_sign)
plot(fitted(lmap_sign),resid(lmap_sign),xlab = "Fittings",ylab = "Residuals",main = "Tukey-Anscombe-Plot of significant airpollution variables")
qqPlot(resid(lmap_sign),dist="norm",mean=mean(resid(lmap_sign)),sd=sd(resid(lmap_sign)))
```
All variables are now highly significant. The model also looks well, all criterias fullfilled. 

